### 2025-07-04 index.qmd
20250704 - log chunk execution times

>>>>

```{r setup}
#| include: false

# Enable automatic chunk timing logging to GitHub Actions
knitr::opts_chunk$set(time = TRUE) # Apply to ALL chunks globally

# Null coalescing operator
`%||%` <- function(a, b) if (!is.null(a)) a else b

# Setup output file
log_file <- "chunk-times.txt"
if (file.exists(log_file)) file.remove(log_file)

# Define hook
knitr::knit_hooks$set(time = function(before, options) {
  if (before) {
    options$start_time <- Sys.time()
  } else {
    elapsed <- difftime(Sys.time(), options$start_time, units = "secs")
    label <- options$label %||% "<unnamed>"
    msg <- sprintf("Chunk `%s` ran in %.2f seconds.", label, as.numeric(elapsed))

    # Log to GitHub Actions via stdout (so it's not suppressed)
    cat(sprintf("::notice title=Chunk Time::%s\n", msg))

    # Also log to file
    cat(msg, file = log_file, append = TRUE, sep = "\n")
  }
})
```
